A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-09 sections/queueing_model/main.tex
Minor changes on queueing section

\section{A queueing model with 2 consecutive buffer centres}\label{sec:queueing_model}
% TODO: If this is to be one paper maybe the first two paragraphs do not need to
% include so much details or even better omit some of the details in the game
% overview section.
In this section, a more in-depth explanation of the queueing model shown in 
figure \ref{fig:diagram_of_queueing_system} will be given.
This is a queueing model that consists of two waiting zones; the parking space
and the hospital waiting space.

@@

        % The label between the lines for T
        \node[anchor=north] at (5.15, 0.80 cm) {\small{\( T \)}};

@@

The model consists of two types of individuals; type 1 and type 2.
% TODO: Decide whether to define type 1, 2 only in queueing section, only in game section, or both
Type 2 individuals are non-urgent patients arriving in ambulances (i.e. patients
in ambulances ).
and type 1 individuals are individuals arriving from other sources 
(e.g walk-in patients, urgent patients from either walk-ins or ambulances).
Type 1 individuals arrive instantly at the hospital's waiting space and wait to
receive their 
service. 
Type 2 individuals arrive at the parking space and wait there until they are 
allowed to move to the hospital.
They are allowed to proceed only when the number of 
individuals in the hospital is less than the
pre-determined threshold \(T\).
When the number of individuals is equal to or exceeds this threshold, all 
type 2 individuals that arrive will stay 
\textit{blocked} in the parking space until the number of patients in 
the hospital falls below \(T\). 
This is shown diagrammatically in Figure \ref{fig:diagram_of_queueing_system}.
The parameters of the described queueing model are:

@@

In order to consider this model numerically an adjustment needs to be made. 
The problem defined above assumes no upper boundary to the number of individuals 
that can wait in the hospital or for the ones that are blocked in the parking 
space. 
Therefore, a different state space \( \tilde S \) is constructed where 
\( \tilde S \subseteq S \) and there is a maximum allowed number of individuals 
\(N\) that can be in the hospital and a maximum allowed number of individuals 
\(M\) that can be blocked in the parking space:

@@

Using vector \(\pi\) there are numerous performance measures of the model that 
can be calculated. 
The following equations utilise \(\pi\) to get performance measures on the 
average number of patients at certain sets of state:

\begin{itemize}
    \item Average number of patients in the entire system: 
        \[L = \sum_{i=1}^{|\pi|} \pi_i (u_i + v_i)\]
    \item Average number of patients in the hospital: 
        \[L_H = \sum_{i=1}^{|\pi|} \pi_i v_i\]
    \item Average number of patients in the parking space:
        \[L_A = \sum_{i=1}^{|\pi|} \pi_i u_i\] 
\end{itemize}

Consequently, there are some additional performance measures of interest that
are not as straightforward to calculate.
Such performance measures are the mean waiting time in the system (for both 
type 1 and type 2 individuals), the mean time blocked in the parking space (only
valid for type 2 individuals) and the proportion of individuals in the hospital
whose waiting time falls within a predefined time target (for both types).

>>>>

\section{A queueing model for the ED-EMS interface}\label{sec:queueing_model}
% TODO: If this is to be one paper maybe the first two paragraphs do not need to
% include so much details or even better omit some of the details in the game
% overview section.
In this section, a more in-depth explanation of the queueing model shown in 
figure \ref{fig:diagram_of_queueing_system} will be given.
This is a queueing model that consists of two waiting zones; the parking space
and the hospital waiting space.

@@

        % The label between the lines for T
        \node[anchor=north] at (5.15, 0.81 cm) {\small{\( T \)}};

@@

The model consists of two types of individuals; type 1 and type 2.
% TODO: Decide whether to define type 1, 2 only in queueing section, only in game section, or both
Type 2 individuals are non-urgent patients arriving in ambulances (i.e. patients
in ambulances that would not be at risk if they were blocked at the parking 
space) and type 1 individuals are individuals arriving from other sources 
(e.g walk-in patients, urgent patients from either walk-ins or ambulances).
Type 1 individuals arrive instantly at the hospital's waiting space and wait to
receive their service. 
Type 2 individuals arrive at the parking space and wait there until they are 
allowed to move to the hospital.
They are allowed to proceed only when the number of 
patients in the hospital is less than the
pre-determined threshold \(T\).
When the number of individuals is equal to or exceeds this threshold, all 
type 2 patients that arrive will stay 
\textit{blocked} in the parking space until the number of patients in 
the hospital falls below \(T\). 
This is shown diagrammatically in Figure \ref{fig:diagram_of_queueing_system}.
The parameters of the described queueing model are:

@@

In order to consider this model numerically an adjustment needs to be made. 
The problem defined above assumes no upper boundary to the number of patients 
that can wait in the hospital or to the ones that are blocked in the parking 
space.
Therefore, a different state space \( \tilde S \) is constructed where
\( \tilde S \subseteq S \) and there is a maximum allowed number of patients 
\(N\) that can be in the hospital and a maximum allowed number of ambulances 
\(M\) that can be blocked in the parking space:

@@

Using vector \(\pi\) there are numerous performance measures of the model that 
can be calculated. 
The following equations utilise \(\pi\) to get performance measures for the 
average number of patients at the different nodes of the queueing model:

\begin{itemize}
    \item Average number of patients in the entire system: 
        \[L = \sum_{i=1}^{|\pi|} \pi_i (u_i + v_i)\]
    \item Average number of patients in the hospital: 
        \[L_H = \sum_{i=1}^{|\pi|} \pi_i v_i\]
    \item Average number of patients/ambulances in the parking space:
        \[L_A = \sum_{i=1}^{|\pi|} \pi_i u_i\] 
\end{itemize}

Consequently, there are some additional performance measures of interest that
are not as straightforward to calculate.
Such performance measures are the mean waiting time in the system (for both 
type 1 and type 2 individuals), the mean time blocked in the parking space (only
valid for type 2 individuals) and the proportion of individuals in the hospital
whose waiting time falls within a predefined time target (for both types).
% TODO: Explain why these performance measures are needed? (for the game)
